---
title: "1.1-Videos extraction"
author: "Alberto Agudo Domínguez"
date: '2022-07-17'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

---

```{r}
library(tidyverse)
library(RSelenium)

options(scipen = 9999)
```

## 1) Select which tweets might contain videos

```{r}
# Read our tweets dataframe:
tweets_df <- read_csv("../data/clean/tweets_df.csv", col_types = cols(status_id = "c"))

# Get all tweets that might contain a video
# (Those for which media_type is "photo" are restrictive. Rather, we should
# get all videos that include a link in the tweet):
tweets_df$has_https <- grepl("https.*", tweets_df$text)

round(sum(tweets_df$has_https) / nrow(tweets_df) * 100, 2) 

tweets_df
```

94% of the tweets contain a link. It could be to either other websites, or media. Hence, there is a big source of information here.

## 2) Create the Selenium search:

```{r message=FALSE, warning=FALSE}
# Set up the download directory:
download_dir <- normalizePath("../data/raw/audio_files") 

# Set firefox preferences for downloads location
fprof <- makeFirefoxProfile(list(browser.download.manager.showWhenStarting = FALSE,
                                 browser.download.alwaysOpenPanel = FALSE,     
                                 browser.download.dir = download_dir,
                                 browser.helperApps.neverAsk.saveToDisk="text/csv",
                                 browser.helperApps.neverAsk.saveToDisk = "text/csv",
                                 browser.download.folderList = 2L))

# Initialize the browser
rD<- rsDriver(browser = c("firefox"), extraCapabilities = fprof)
driver <- rD$client

# Check that it is navigating properly
url <- "https://f2mp.com/twitter"
driver$navigate(url)
```


```{r}
# Set up the selectors:
css <- list()

css$search_box <- '#txt-url'
css$search_btn <- '#btn-start'
css$audio_mode_btn <- '.active+ li a'
css$audio_mode_btn2 <- '.nav-tabs > li:nth-child(2) > a:nth-child(1)'
css$process_audio_btn <- '.btn-download-audio'
css$error_message <- '#result-errors > span:nth-child(3)'
css$download_btn <- 'button.btn-success:nth-child(2)'
css$close_download_btn <- '.btn-default'
```



```{r}
# Search procedure per each tweet
for (row in 1:nrow(tweets_df)){
  print(paste0("ROW: ", row))
  print(final_tweets[[row, "text"]])
  
  has_https <- final_tweets[[row, "has_https"]]
  print(paste0("HAS HTTPS: ", has_https))
    # If the tweet does not have a link, go to the next one
    if (has_https){
  
      status_id <- final_tweets[[row, "status_id"]]
      tweet_link <- final_tweets[[row, "status_url"]]
      
      print(paste0("STATUS ID: ", status_id))
      print(paste0("LINK: ", tweet_link))
      
      # Get the directory to compare at the end and get the name of the new files
      beginning_dir <- list.files(download_dir)
      
      # Items for the search
      search_box <- driver$findElement(using = "css", value = css$search_box)
      search_btn <- driver$findElement(using = "css", value = css$search_btn)
      
      # Type the URL and find the item
      search_box$sendKeysToElement(list(tweet_link))
      search_btn$clickElement()
      
      # Give enough time before checking whether there is an error
      Sys.sleep(1.5)
      
      # Click the audio mode for download
      audio_mode_btn <- driver$findElement(using = "css", value = css$audio_mode_btn2)
      audio_mode_btn$clickElement()
      
      # Check that there have not been any errors:
      error_message <- driver$findElement(using = "css", value = css$error_message)
      error_text <- error_message$getElementText()[[1]]
      
      # This error appears when the file is not a video. In that case, the code
      # does not run and we jump to the following tweet
      while (error_text == ""){
        
        Sys.sleep(0.1)
        # Start processing the mp3 file
        process_audio_btn <- driver$findElement(using = "css", value = css$process_audio_btn)
        process_audio_btn$clickElement()
        Sys.sleep(0.5)
        
        # Find the download button
        download_btn <- driver$findElement(using = "css",
                                           value = css$download_btn)
        
        download_text <- download_btn$getElementText()[[1]]
        
        # Wait until the audio has been processed
        while ((download_text == "") & (error_text == "")){
          
          Sys.sleep(2)
          
          # Check again that there is not any error after applying the search:
          error_message <- driver$findElement(using = "css", value = css$error_message)
          error_text <- error_message$getElementText()[[1]]
          
          # Sometimes you need to click again
          audio_mode_btn <- driver$findElement(using = "css", value = css$audio_mode_btn2)
          audio_mode_btn$clickElement()
          process_audio_btn <- driver$findElement(using = "css", value = css$process_audio_btn)
          process_audio_btn$clickElement()
          download_btn <- driver$findElement(using = "css",
                                           value = css$download_btn)
          download_text <- download_btn$getElementText()[[1]]
          print("Waiting for download button to appear")
        }
        
        # Sometimes the search returns an error after clicking the item
        # In that case, break the while loop
        if (error_text != ""){
          break
        }
        
        # Once the audio has been processed, download it:
        download_btn$clickElement()
        
        # Close download
        close_button <- driver$findElement(using = "css", 
                                           value = css$close_download_btn)
        close_button$clickElement()  
        
        # Finally, get the name of the new file and rename it according to 
        # the status id of the tweet (introduce a while loop to wait for the download)
        end_dir <- list.files(download_dir)
        new_file <- setdiff(end_dir, beginning_dir)
        while ((identical(new_file, character(0))) | (length(new_file) == 2)){
          Sys.sleep(1)
          end_dir <- list.files(download_dir)
          new_file <- setdiff(end_dir, beginning_dir)
          print("Waiting for file to be downloaded")
        }
        
        file.rename(from = paste0(download_dir, "/", new_file), 
                    to = paste0(download_dir, "/", status_id, ".mp3"))
        
        # Finally, change the error text to exit the loop
        error_text <- "Finished"
        
      }
      
        # Clean search box for next step
        search_box <- driver$findElement(using = "css", value = css$search_box)
        search_box$clearElement()
        
        # Wait a bit to avoid overload:
        Sys.sleep(0.2)
    }
  }
```




```{r}
# First, let us see which of the tweets had a video:
final_mp3s <- list.files(download_dir)
clean_mp3s <- sapply(final_mp3s, FUN = function(x) substr(x, 1, nchar(x) - 4)) %>% 
  unname(.)

tweets_df$has_video <- tweets_df$status_id %in% clean_mp3s

print(paste("There are", sum(tweets_df$has_video), "tweets that contain videos."))
```

After the download I will manually check which audios should be discarded. Some videos only show people in a meeting, or an event, so they are not useful to transcribe the audios to text.

```{r}
# Out of those videos, which ones are worth transcribing (i.e., they are not simply a video without people speaking)?
# In the order of added audios
# 0: No audio, 
# 0.25: There are no politicians speaking (or very marginally)
# 0.33: There is a politician, but too many people arguing at the same time
# 0.5: Bad quality audio (like an interview with a lot of noise, or sometimes
#   a politician interrupts the speaker),
# 0.75: Good audio, but there are other politicians or moderators speaking at some point (or high music, even though the voice can be properly heard)
# 1: High quality audio, only one speaker from the party.
# -1: Duplicated
# -2: Audio not in Spanish

# Create an excel where we can keep track of which audio are we listening to,
# and categorize its quality:
#remaining_audios <- length(final_mp3s) - length(audio_quality)
#
##audio_quality <- c(audio_quality, rep(NA, remaining_audios))
#
#audios_df <- data.frame(final_mp3s = apply(tweets_df[tweets_df$has_video == T, 
#                                                     "status_id"], 
#                                           MARGIN = 1, 
#                                           FUN = function(x) paste0(x, ".mp3")), 
#                        audio_quality)
#
#rio::export(audios_df, "../data/raw/audios_df.xlsx")


# Export also the tweets_df dataframe now that we know which tweets contained videos:
write.csv(tweets_df, "../data/clean/tweets_df.csv", row.names = F)
```


Lastly, let us close the driver and browser:

```{r}
driver$close()
rD$server$stop()
```




