---
title: "0 - Political videos extraction"
author: "Alberto Agudo Domínguez"
date: '2022-05-24'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r message=FALSE, warning=FALSE, include=FALSE}
# General requests packages:
library("httr")
library("jsonlite")
# Twitter API package: 
library("rtweet")
# General manipulation libraries:
library("stringr")
library("tidyverse")
```

In this rmarkdown file I will deploy the requests to the Twitter API necessary to extract the political videos of the Spanish election campaign of November 2019.

## 1. Twitter API setup

First, let us load the Twitter API key:

```{r, eval = FALSE}
#authentication <- list(consumer_key = "API_key",
#                 consumer_secret = "API_key_secret",
#                 access_token = "access_token",
#                 access_token_secret = "access_token_secret")
#save(authentication, file = "tw_authentication.rda")

load("tw_authentication.rda")
```

Now open the session with the token:
```{r}
twitter_token <- create_token(app = "Agudo API Data Science", 
                              consumer_key = authentication$consumer_key,
                              consumer_secret = authentication$consumer_secret,
                              access_token = authentication$access_token,
                              access_secret = authentication$access_token_secret)
```

Basic proof that the API is working:
```{r}
lookup_users("LSEnews")$screen_name
```

### Downloading recent tweets from a specific user

There is a function within rtweet to retrieve the timeline of tweets of a specific user. We would like to get back to the tweets of November 2019. Nevertheless, there is a maximum of 3,200 tweets per account. Hence, we might have to signal directly the tweets that we need.

First, let us determine the Twitter accounts of the political candidates and their parties that we would like to investigate:

```{r}
# We will create a list of parties and their respective political candidates and official accounts.
# Structure -> Party name in lower case letters (name of vector). Then a vector with:
# 1) Name of main political candidate
# 2) Name of official account
# Additional: Other important political candidates or political accounts
users <- list("vox" = list("political_candidate" = "Santi_ABASCAL", 
                           "official_party_account" = "vox_es",
                           "additional_politicians" = c(""),
                           "additional_party_accounts" = c("")))
```





```{r}
tweets_abascal <- get_timeline(users$vox$political_candidate, n = 3200)
tweets <- get_timeline("JoeBiden", n = 1000)
```

